---
title: "03_DataPreparation"
output: pdf_document
---


# Data Preparation

## Feature Engineering

##   External Data - Continents

Country based visualizations can also be difficult to interpret as there are many country names. For this, continent data that mapped countries from outside was found and merged with enrollment data.



##  External Data - Step Activity Metadata 
We will create a map list which includes names, types and step_id. 



```{r}
head(run_3.step.metadata)
```
Then, we will merge with step activity data frames.

```{r}
df.filtered <- step_activity %>% dplyr::filter(!run_id %in% c(1,2)) # run 1  and run 2 are not same structure
df.filtered <-  merge(x= df.filtered, y = run_3.step.metadata, by.x = "step", by.y="step_id", all.x = TRUE)

```


##  Calculating Time Difference


In order to achieve our business goal, we need to calculate the total elapsed time. We can find difference time between **first_visited_at** and **last_completed_at**.Since some records do not have a last time date, we will specify their value as 0. 


It was stated in one of the business objective that the reading date would be estimated. 
It will be better in terms of user experience to estimate this estimate in half-minute intervals instead of seconds. We need to round the data in seconds to numbers such as 6.30 minutes, 7 minutes. The name of this newly created column will be called **elapsed_time**.

These operations were implemented in `munge/03-FeatureEngineering.R`


## Filter Data Frame

We only need to filter records that have a last completed date.

```{r}

df.filtered  <- df.filtered  %>% filter(diff_second != 0)

```