---
title: "06_DataUnderstanding"
output: pdf_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
```


#  Data Understanding

## Exploratory Data Analysis


## Plot Reading Time in Seconds For Each Article
```{r}
ggplot(data= df.article , aes(x = diff_second, group=step, color=step)) +
  geom_boxplot(position = 'dodge')+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  ggtitle("Plot Reading Time For Each Article")
ggsave(file.path('graphs', 'reading_time_diff_second_by_step.png'))
```

As you can see, each article has a different range.

###  Calculate Average Article Reading Time

One of the business objectives was average article read time. It should be noted that **geometric mean** is used to reduce the effect of outlier values.
The function was implemented in `lib/helpers.R` file.

```{r}
## Calculate geometric mean for every article
df.article.mean <- df.article %>% group_by(step) %>% summarise(mean_diff_second = helper.geo_mean(diff_second))

```




###  Plot Average Article Reading Time

```{r}
ggplot(data= df.article.mean , aes(x = step, y=mean_diff_second)) +
  geom_col(position = 'dodge')+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  ggtitle("Average Article Reading Time")
ggsave(file.path('graphs', 'article_average_reading_time.png'))
```

According to the bar graph, the step with the highest average is **step 2.18**. The name of this step is *"Bitcoin: a cryptocurrency *. This topic can be considered interesting. Looking at the lowest averages are 1.18 and 3.20 which names are *"Recapping our exploration of privacy"* and *"Wrapping up"*. The common feature of these 2 steps is that it is a summary article. From this graph, it can be interpreted that users are not very interested in summarizing articles.


### Select an Article and Plot

Since the length of the articles is not known, each article has its own distribution in terms of reading time. Therefore, making an analysis on all data will create misleading results. 2 articles will be chosen at random and continued over them.



```{r}
df.article.filtered <- df.article %>% filter(step  %in% c("1.3","2.16"))
```



## BoxPlot Elapsep Time by age

```{r}
ggplot(data= df.article.filtered, aes(x = elapsed_time, group=age_range, color=age_range)) +
  geom_boxplot(position = 'dodge')+
  facet_wrap(~step+step_name , scales = "free", ncol = 2)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  ggtitle("Reading time of articles by age")
ggsave(file.path('graphs', 'article_13_216_elapsed_time.png'))
```

According to the graph, it seems that there are too many outliers in people of unknown age.
It seems that people over the age of 65 give importance to the subject of "Is your mobile phone spying on you" .


### Age Distribution

```{r}
ggplot(data= df.article.filtered, aes(x = age_range, color=age_range)) +
  geom_bar(alpha = 0.3)+
  facet_wrap(~step+step_name , scales = "free", ncol = 2)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  ggtitle("Age Distribution")
ggsave(file.path('graphs', 'article_13_216_elapsed_time_age_dist.png'))
```
As you can see in the bar graph, there is a lot of data of unknown age.



## Plot Elapsed Reading Time by employment status
```{r}
ggplot(data= df.article.filtered, aes(x = elapsed_time, group=employment_status, color=employment_status)) +
  geom_boxplot(position = 'dodge')+
  facet_wrap(~step+step_name, scales = "free", ncol = 2)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  ggtitle("Elapsed Reading time of articles by employment status")
ggsave(file.path('graphs', 'article_13_216_elapsed_time_employment_status.png'))
```


It seems that students give less importance to "Is your mobile phone spying on you" than other employment statuses. The median value of this is very low compared to others


## Plot Elapsed Reading Time by Employment Area
```{r}
ggplot(data= df.article.filtered %>% filter(step=="1.3"), aes(x = elapsed_time, group=employment_area, color=employment_area)) +
  geom_boxplot(position = 'dodge')+
  facet_wrap(~step+step_name, scales = "free")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  ggtitle("Elapsed Reading Time of Articles by Employment Status")
ggsave(file.path('graphs', 'article_13_216_elapsed_time_employment_area.png'))
```
As can be seen from the graphics, the time spent on the article varies according to the demographic information of the people and the subject of the article.
