---
title: "07_DataPreparation"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
```


#  Data Preparation

The random state ensures that the splits that you generate are reproducible.

```{r}
set.seed(123) # random state
```


## Feature Selection


According to the features extracted from the analysis, a total of 7 independent variables will be used in the first model.

```{r}
df_model <- df.article %>% select(step,elapsed_time,gender,age_range, highest_education_level,employment_status, employment_area)
```


## Filter Unknown

During Exploratory Data Analysis, it was determined that the data with the value "Unknown" had too many outliers. These values should be filtered.

```{r}
df_model <- df_model %>% filter(age_range != "Unknown") %>% filter(highest_education_level != "Unknown") %>% filter(employment_status != "Unknown") %>% filter(gender != "Unknown") %>% filter(employment_area  != "Unknown")
```


## Reset Factor Levels

The type of data we filtered was factor. Therefore, you need to reset our factor level.

```{r}
df_model$step <- as.factor(as.character(df_model$step))
df_model$gender <- as.factor(as.character(df_model$gender))
df_model$age_range <- as.factor(as.character(df_model$age_range))
df_model$highest_education_level <- as.factor(as.character(df_model$highest_education_level))
df_model$employment_status <- as.factor(as.character(df_model$employment_status))
df_model$employment_area <- as.factor(as.character(df_model$employment_area))
```

### Train-Test Split

To measure the success of our model, we need to separate our data into training and testing.We will split data into 80 percent for training, 20 percent for validation.


```{r}

train.index <- createDataPartition(df_model$elapsed_time, p = .8, list = FALSE)
train <- df_model[ train.index,]
test  <- df_model[-train.index,]
```


